### 2014-06-02 scratchwork/makenew.mixEM.Rmd
updated variational em

penloglik = function(pi, matrix_lik, prior){
  m  = t(pi * t(matrix_lik)) # matrix_lik is n by k; so this is also n by k
  m.rowsum = rowSums(m)
  loglik = sum(log(m.rowsum))
  priordens = sum((prior-1)*log(pi))
  return(loglik+priordens)
}

@@

```

@@

```{r}
  system.time(res1<-mixEM(lik,prior,pi.init))
  system.time(res2<-mixEM2(lik, prior, pi.init))
  options(digits=13)
  res1
  res2
```

>>>>

penloglik = function(pi, matrix_lik, prior){
  m  = t(pi * t(matrix_lik)) # matrix_lik is n by k; so this is also n by k
  m.rowsum = rowSums(m)
  loglik = sum(log(m.rowsum))
  subset = (prior-1) != 0
  priordens = sum((prior-1)[subset]*log(pi[subset]))
  return(loglik+priordens)
}

@@

#as above but with initial iterations done with smaller sample sizes
#and tolerance set according to sample size
mixEM3 = function(matrix_lik, prior, pi.init = NULL,tol=1e-7, maxiter=5000){
  if(is.null(pi.init)){
    pi = rep(1/k,k)# Use as starting point for pi
  } 
  n = nrow(matrix_lik)
  if(n>1000){       
    res = squarem(par=pi.init,fixptfn=fixpoint, objfn=penloglik,matrix_lik=matrix_lik[1:1000,], prior=prior, control=list(maxiter=maxiter,tol=1e-3,trace=TRUE))
    pi.init = res$par
    print(pi.init)
  }
  res = squarem(par=pi.init,fixptfn=fixpoint, objfn=penloglik,matrix_lik=matrix_lik, prior=prior, control=list(maxiter=maxiter,tol=tol,trace=TRUE))
  return(list(pihat = res$par, B=res$value.objfn, 
              niter = res$iter, converged=res$convergence))
}
```

@@

```{r}
  system.time(res1<-mixEM(lik,prior,pi.init))
  system.time(res2<-mixEM2(lik, prior, pi.init))
   system.time(res3<-mixEM3(lik, prior, pi.init))
  options(digits=13)
  res1
  res2
  res3
```

What we found: subsetting by initially running on only 1000 data points
did not work so well - it converged to a value of pi that was pretty different from
the mle for all 100,000 so didn't really save anything.

This section just to run 100 times to see if any warnings results
```{r}
#   options(warn=2)
#    for(i in 1:100){
#      set.seed(i)
#     z0 = rnorm(sampsize,0,1)
#     sd=c(1,2,4,8,16,32)
#     prior=c(1,1,1,1,1,1)
#     pi.init=c(1,1,1,1,1,1)/6
#     lik = t(vapply(z0,dnorm,sd,sd=sd))
#     print(i)
#     res2[[i]]<-mixEM2(lik, prior, pi.init)
#     }
```

### 2014-06-02 tests/largedata.Rmd
updated variational em

```{r}
  library(ashr)
  set.seed(111)
  z = rnorm(100000)
  z.ash = ash(z,1)
  z.ash2 = ash(z,1,method="fdr")
```

>>>>

```{r}
  require(ashr)
  eg5 = matrix(scan("~/Dropbox/eg.j5.txt"), byrow=TRUE, nrow=2)
  temp1=ash(eg5[1,],eg5[2,],cxx=FALSE)
  temp2=fast.ash(eg5[1,],eg5[2,],prior="nullbiased",pointmass=TRUE,gridmult=2,cxx=FALSE)

```

```{r}
  eg9 = matrix(scan("~/Dropbox/eg.j9.txt"), byrow=TRUE, nrow=2)
  temp1=ash(eg9[1,],eg9[2,],cxx=FALSE)
  temp2=fast.ash(eg9[1,],eg9[2,],prior="nullbiased",pointmass=TRUE,gridmult=2,cxx=FALSE)

```

```{r}
  library(ashr)
  set.seed(111)
  z = rnorm(100000)
  z.ash = ash(z,1,cxx=FALSE,method="fdr")
  z.ash2 = ash(z,1,method="fdr")
```
